Fast, Scalable Phrase-Based SMT Decoding

### 2016-01-28 acl.2016/acl2016.tex
fixing segfault on thrud

Features functions are the $h_m$ in Equation~\ref{eq:Log-Linear}, calculating a score for each hypothesis which is then weighted and summed to give an overall score.

Standard feature functions in the phrase-based model include:
\begin{enumerate}
  \item log transforms translation model probabilities, $p_{TM}(t|s) $ and $p_{TM}(s|t)$, and word-based translation probabilities $p_w(t|s)$ and $p_w(s|t)$,
  \item log transforms of the lexicalized re-ordering probabilities,
  \item log transforms of the target language model probability $p(t)$, 
  \item a distortion penalty
  \item a phrase-penalty,
  \item a word penalty,
  \item an unknown word penalty.
\end{enumerate}
%which we have suffixed with $_{TM} $ to avoid confusion with the overall model probability $ p(t|s) $ and $ p(s|t)$.

@@

Load-on-demand 'binary' phrase-tables are often used for MT deployment due to the advantages of fast loading and fast querying speed, and because they can be used with large phrase-tables. We therefore focus on optimizing decoding speed with these phrase-tables, specifically the Probing PT.

>>>>

Features functions are the $h_m$ in Equation~\ref{eq:Log-Linear}, calculating a score for each hypothesis.

The standard feature functions in the phrase-based model include:
\begin{enumerate}
  \item log transforms translation model probabilities, $p_{TM}(t|s) $ and $p_{TM}(s|t)$, and word-based translation probabilities $p_w(t|s)$ and $p_w(s|t)$,
  \item log transforms of the lexicalized re-ordering probabilities,
  \item log transforms of the target language model probability $p(t)$, 
  \item a distortion penalty
  \item a phrase-penalty,
  \item a word penalty,
  \item an unknown word penalty.
\end{enumerate}
%which we have suffixed with $_{TM} $ to avoid confusion with the overall model probability $ p(t|s) $ and $ p(s|t)$.

@@

Load-on-demand \emph{'binary'} phrase-tables are often used for MT deployment due to their fast loading and fast querying speed, and because they can be used with large phrase-tables. We therefore focus on optimizing decoding speed with these phrase-tables, specifically the Probing PT.
